---
title: "Vignette RP"
author: "Ximeng Zhao"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette RP}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The RP package can be used to analyze the data from the US National Highway Traffic Safety Administration's. The R package is available on my Github and can be used by typing the following commands:

```r
devtools::install_github("https://github.com/SimonFans/RP")

```
## Functions 

There are five functions that can be utilized for the analysis

-fars_read()
-make_filename()
-fars_read_years()
-fars_summarize_years()
-fars_map_state()

The function "fars_read()" implements the read methods to a csv file.
```{r, echo=FALSE}
data<-fars_read(filename="./accident_2014.csv.bz2")
```

The function "make_filename()" creates a filename for a .csv.bz2 based on the year that you input.
```{r, echo=FALSE}
data_filename<-make_filename(2014)
```

The function "fars_read_years()" returns a list of dataframes with MONTH and year columns based on data in "accident_<year>.csv.bz2" files.
```{r, echo=FALSE}
month_year<-fars_read_years(2014)
```

The function "fars_summarize_years()" counts number of accidents per month and year.
```{r, echo=FALSE}
accidents_summary<-fars_summarize_years(2013:2015)
```

The function "fars_map_state()" accepts a state number and year and plots the accidents in a simple map.
```{r, echo=FALSE}
accidents_state_year<-fars_map_state(35, 2014)
```

The accidents data from 2013 to 2015 are available in both data folder and RP directory. 



